\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2017-01-20 redaction/dhp_sept2016.tex
changement mineur

One may be concerned that the specification of Equations (\ref{eq:model_nlI}}) or (\ref{eq:model_IetA}) might be subject to endogeneity bias, as the price set be the exporter may vary depending on the transport costs burden. Notably based on the pricing-to-market behavior of firms (see \citealp{Krugman-87}), we cannot exclude that the export price set by the firm ($\widetilde{p}_{ik}$) is partly endogenous to the size of transport costs (for instance, the exporting firm absorbing (part of) the transport costs by reducing the fas price). However, we do not view this as raising an endogenity problem as this does not change our dependent variable of interest, the gap between the cif and the fas prices. Except in the choice between air and ocean transport (that is beyond our scope of analysis), the exporting firm has no influence on the cif-fas price gap. Otherwise stated, the firm chooses an export price and a transport mode, the gap between the export price declared to the custom data and the import price recorded by the US administration is beyond her control. In this respect, we are confident that our estimation strategy is immune from endogeneity problems. \smallskip

>>>>

One may be concerned that the specification of Equations (\ref{eq:model_nlI}) or (\ref{eq:model_IetA}) might be subject to endogeneity bias, as the price set be the exporter may vary depending on the transport costs burden. Notably based on the pricing-to-market behavior of firms (see \citealp{Krugman-87}), we cannot exclude that the export price set by the firm ($\widetilde{p}_{ik}$) is partly endogenous to the size of transport costs (for instance, the exporting firm absorbing (part of) the transport costs by reducing the fas price). However, we do not view this as raising an endogenity problem as this does not change our dependent variable of interest, the gap between the cif and the fas prices. Except in the choice between air and ocean transport (that is beyond our scope of analysis), the exporting firm has no influence on the cif-fas price gap. Otherwise stated, the firm chooses an export price and a transport mode, the gap between the export price declared to the custom data and the import price recorded by the US administration is beyond her control. In this respect, we are confident that our estimation strategy is immune from endogeneity problems. \smallskip
